\documentclass[letter]{article}
\usepackage[monocolor]{ahsansabit}

\title{Honors Multivariable Calculus : : Class 36}
\author{Ahmed Saad Sabit, Rice University}
\date{\today}

\begin{document}
\maketitle

Suppose $\vec{F}$ is defined on all $\mathbb{R}^{2}$ and curl $\vec{F}$ is $0$ everywhere. Then 
\[
\oint _C \vec{F} \cdot \mathrm{d} \vec{s} = \int_{R}^{} \text{curl} \vec{F} = 0 
\]
We can conclude that $\oint$ is 0 then $\vec{F}$ is conservative.

\df{
A domain $D \subset \mathbb{R}^{n}$ is simply connected if it is path-connected and every loop in $D$ can be "filled in" without leaving $D$. 
}

Discussion on what is a simply connected loop is being done. It has to be some funny topological problem. Can we contract a loop into a single point without running into a domain issue? Well in $\mathbb{R}^{3}$ if we have a hole at $x,y,z=0,0,0$ then a loop can be moved away from that point and contracted to 0.

\df{
A region $R \subset \mathbb{R}^{2}$ is a "simple region" (made up) if it can be described both as 
\[
R = \{(x,y) : a_1 \le x \le b_1, f_1(x) \le  y \le f_2(x)\}  
\] For some continuous functions $f_1, f_2$ satisfying $f_1(x) \le  f_2(x) \, \forall x \in [a_1,b_1]$. AND as 
\[
R = \{(x,y): a_2 \le y \le b_2, g_1(y) \le x\le g_2(y) \} 
\] For some continuous functions $g_1, g_2$ satisfying $g_1(y)\le  g_2(y) \, \forall y \in [a_2,b_2]$. 
Box, disk. }

\section*{Vector Surface Integral}
Let $\vec{F}$ in $\mathbb{R}^{3}$. The oriented surface be chosen $S$. Choose $S$ to have one side and 
\[
\int_S \vec{F} \cdot \mathrm{d} \vec{S}
\] 
is integral of $\vec{F}$ over $\vec{S}$. 

Simplest case is to consider a flat constant field. Take a plan and we have some surface $S$ on that plane and it has a positive side. 

\end{document}
